\documentclass{resume}
\usepackage[utf8x]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}
\urlstyle{same}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{ORÇUN ÖZDEMİR}

\basicInfo{
  \linkedin[orçunözdemir]{https://linkedin.com/in/orçunözdemir} \textperiodcentered\ 
  \github[0x01h]{https://github.com/0x01h}
  \textperiodcentered\ 
  \stackoverflow[0x01h]{https://stackoverflow.com/users/9389666/0x01h}}

\basicInfo{
  \email{benorcunozdemir@gmail.com} \textperiodcentered\ 
  \phone{(+90) 537 879 68 56}}
  
\basicInfo{
  \faHome{ Istanbul, Turkey}}
  
\section{\faUser\ Profile}
Love to work on exciting data-driven projects and AI applications. 
  
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Istanbul Technical University (ITU)}, Istanbul, Turkey}{2014 -- 2019}
\textit{B.S.} in Computer Engineering (CE)

\datedsubsection{\textbf{Giresun High School of Science}, Giresun, Turkey}{2010 -- 2014}
Presented a project in 4006 - TUBITAK Science Fair. Ranked 3310th among nearly 2 millions of participants in the national college entrance exam.

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Trendyol} @Istanbul, Turkey}{May, 2019 -- Present}
\role{Data Engineer}{}
Data oriented tasks and R&D projects in Trendyol which is the leading e-commerce company in Turkey and strategic partner of Alibaba.\vspace{2ex}

Experiences with Scala, Spark, Hadoop, TensorFlow, Keras, Jupyter/Zeppelin Notebooks, Hive, PrestoDB, Jenkins, Kubernetes, cloud platforms and many other open source Apache softwares on big data.

\datedsubsection{\textbf{Deep Learning Türkiye} @Turkey}{April, 2019 -- Present}
\role{Member}{}
Member of Turkey's leading AI community.

\datedsubsection{\textbf{Sociality.io} @Istanbul, Turkey}{June, 2018 -- Jan, 2019}
\role{Software Developer}{}
Developed and maintained softwares to improve Sociality.io's all in one social media platform. Worked on RESTful APIs, web frameworks, bug bounty program and machine learning solution for sentiment analysis.\vspace{2ex}

Experiences with PHP, Laravel, MongoDB, Docker, Redis, and ElasticSearch.

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, Scala, Haskell, C/C++, PHP, HTML/CSS, JS
  \item Frameworks: Tensorflow, Keras, Hadoop, Django, Flask, Laravel, Bootstrap, MaterializeCSS, Scrapy
  \item Databases (SQL/NoSQL): PostgreSQL, MongoDB, MySQL, SQLite, Redis
  \item *nix Systems
  \item Jira, Trello
  \item Git, Jenkins, Agile, Scrum, CI/CD/XP practices
\end{itemize}

\clearpage

\section{\faInfo\ Projects}
\begin{enumerate}[parsep=0.5ex]
    \item \href{https://individualsymphony.com}{Individual Symphony}: Music recommendation system based on personalities which is using deep learning genre classifier model and Spotify API. Explore your inside symphony! TensorFlow, Keras, Django, PostgreSQL, and MaterializeCSS are heavily used technologies in development phase.
    \item \href{#!}{Product Unification}: R\&D project to unify different product names of same products in single catalog. Data collection, data processing, developing a deep learning and a Word2Vec model which contains e-commerce vocabulary and implementing a service to make it usable in production composes the project.
    \item \href{https://github.com/0x01h/pyddoz}{PyDDoZ}: PyDDoZ is a powerful, human-friendly DDoS tool using application layer (L7) attack techniques. It has nice logging, proxifying, automated bots requests, randomizing data, multiple HTTP request methods, and many other features! Apply load/stress tests to your web application in various ways easily.
    \item \href{https://github.com/0x01h/channelx}{ChannelX}: Simple anonymous messaging application using WebSockets.
    \item \href{https://github.com/0x01h/hepsiburada-review-scraper}{Hepsiburada Review Scraper}: Hepsiburada review/comment and rating scraper. Turkish text dataset creator for data science and NLP projects. Nearly 30M reviews with category and product links can be crawled and used for text classification, sentiment analysis, text mining, FastText models etc.
    \item \href{https://github.com/0x01h/yozdil-article-scraper-generator}{Yılmaz Özdil Newspaper Article Generator}: Scrape Yılmaz Özdil articles and create Markov model to generate newspaper articles like Yılmaz Özdil. Turkish text dataset creator for data science and NLP projects.
    \item \href{https://github.com/0x01h/zalando-fashion-mnist}{Zalando's Fashion MNIST}: Dockerized Jupyter Notebook CNN solution for Zalando's Fashion MNIST. With the help of this challenge, I learned lots of different CNN achitectures and image processing fundamentals.
    \item \href{https://github.com/0x01h/market-cabbage-stock-simulation}{Market Stock Simulation}: Market cabbage stock simulation written in Python and demonstrated on Jupyter Notebook. Assignment is to simulate the shop for rotting cabbages scenario, and again do the optimal stock size experiments (decide on the optimal stock level of cabbages to keep the number of expired cabbages to a minimum while maintaining the number of customers unable to find a cabbage in stock to 3 in 1000 or less).
    \item \href{#!}{randomyoutubevideo.com}: Esoteric website project that has simple applications written in Python to entertain and interact with visitors on Flask web framework using Bootstrap, JS, JQuery and related technologies.
    \item \href{https://github.com/0x01h/hisim-fanzine}{Hisim Fanzine}: Static fanzine website using turn.js for "Hisim Fanzine".
    \item \href{https://github.com/0x01h/mevzu-records}{Mevzu Records}: Static record label website project of Mevzu Records.
\end{enumerate}

\section{\faBook\ Relevant Coursework}
\begin{itemize}[parsep=0.5ex]
  \item Artificial Intelligence
  \item Discrete Event Simulation
  \item Computer  Security
  \item Software Engineering
  \item Database Management Systems
  \item Object Oriented Programming
  \item Analysis of Algorithms
  \item Data Structures
  \item Computer Organization \& Architecture
\end{itemize}

\section{\faHeart\ Interests}
\begin{itemize}[parsep=0.5ex]
  \item In an Istanbul based art collective, we created fanzines, organized exhibitions, concerts and other events. 
  \item Playing guitar and singing in punk rock band \href{https://open.spotify.com/artist/49GZXacm1ImIxt7vCioeX5}{Hedonistic Noise}.
  \item Strong writing skills on both professional and sarcastic things.
  \item Eastern philosophy and meditation.
\end{itemize}

\end{document}
